---
title: "Voom Test"
output: pdf_document
date: "2024-05-16"
---

```{r}
library(limma)
library(edgeR)
source('voomByGroup.R')
library(ggplot2)
library(tidyverse)
```

# load PBMC1 data

```{r}
counts = readRDS("./PBMC1/counts.rds")
group = readRDS("./PBMC1/group_id.rds")
```

```{r}
group
```

# Data Filtering

```{r}
high_expression_counts = counts[rowSums(counts)>50,]
```

```{r}
filter = (group == 'Moderate' | group == 'HC')
```

```{r}
filtered_counts = high_expression_counts[, filter]
filtered_group = group[filter]
```

# Create DGElist

```{r}
y = DGEList(filtered_counts)
```

```{r}
y$samples$group
y$samples$group = filtered_group
y$samples$group
```

# Calculate Normalizing Factors

```{r}
y = calcNormFactors(y)
```

```{r}
y$samples
```
# Create the design matrix based on group information.

```{r}
group_assignment = y$samples$group
design = model.matrix(~0 + group_assignment)
design
```

# my voom

## Normalize library size R

```{r}
R = y$samples$lib.size * y$samples$norm.factors
```

```{r}
design
```

## Calculate log-cpm

```{r}
Y = t(log2((t(filtered_counts) + 0.5)/(R+1) * 1e6))
```

## Normalize log-cpm

```{r}
Y = normalizeBetweenArrays(Y, method='none')
```

## Equivalent to linear regression

```{r}
#Y1 = Y[, c(1,2,6,7,8,9,10)]
#Y2 = Y[, c(3,4,5)]

Y1 = Y[, c(1,2,3,4,8)]
Y2 = Y[, c(5,6,7)]
mean_Y1 = rowMeans(Y1)
mean_Y2 = rowMeans(Y2)
var_Y1 = apply(Y1, 1, var)
var_Y2 = apply(Y2, 1, var)
n1 = ncol(Y1)
n2 = ncol(Y2)
```

### $\hat{\beta}$

```{r}
beta = cbind(mean_Y1, mean_Y2)
```

```{r}
dim(beta)
```

### $\hat{Y}$

```{r}
Y_hat = beta %*% t(design)
```

```{r}
dim(Y_hat)
```

### $s_g$

```{r}
#s = sqrt(rowSums((Y - Y_hat)^2) / (n1+n2-2))
```

```{r}
s = sqrt(((n1-1) * var_Y1 + (n2-1) * var_Y2) / (n1+n2-2))
```

### $r_g$

```{r}
r = rowMeans(Y) + mean(log2(R+1))-log2(1e6)
```

### s_g^{0.5}

```{r}
s_std = sqrt(s)
```

### lowess()

```{r}
l = lowess(r, s_std,f=0.5)
```

```{r}
plot(r,s_std, xlab="log2( count size + 0.5 )",ylab="Sqrt( standard deviation )",pch=16,cex=0.25)
title("voom: Mean-variance trend")
lines(l,col="red")
```
### approximated func form of lowess

```{r}
f = approxfun(l, rule=2, ties=list("ordered", mean))
```

### lambda

```{r}
lambda = t(t(Y_hat) + log2(R+1))-log2(1e6)
```

### w_gi (predicted square root standard deviance of y_gi)

```{r}
w = 1/(f(lambda)^4)
dim(w) = dim(Y_hat)
dim(w)
```

```{r}
alpha = 0.1
NPMLE_1D_parameter = c(1000, 0.01, 1.0)
NPMLE_2D_parameter = c(80, 80, 0.01, 1.0)
EV_NPMLE_1D_parameter = c(80, 0.01, 1.0)
```

## EPB

### Y_A and Y_B

```{r}
Y_A = Y1
Y_B = Y2
```

### extract sufficient statistics

```{r}
source('EPB.R')
```

```{r}
information_original = information_extractor(Y_A, Y_B)
```

### NPMLE with 1D

```{r}
p_value_1D_NPMLE_original = P_value_1D_NPMLE(information_original, NPMLE_1D_parameter)
```

```{r}
hist(p_value_1D_NPMLE_original)
```

```{r}
length(my_BH(p_value_1D_NPMLE_original, alpha))
```

### NPMLE with 2D

```{r}
NPMLE_2D_result_original = NPMLE_2D(S1_list = information_original$S1_list, S2_list = information_original$S2_list, B1 = NPMLE_2D_parameter[1], B2 = NPMLE_2D_parameter[2], m = information_original$m, n1 = information_original$n1, n2 = information_original$n2, lower_quantile = NPMLE_2D_parameter[3], upper_quantile = NPMLE_2D_parameter[4])
```

```{r}
p_value_2D_NPMLE_original = P_value_2D_NPMLE(information_original, NPMLE_2D_result_original$grid, NPMLE_2D_result_original$mass)
```

```{r}
hist(p_value_2D_NPMLE_original)
```

```{r}
length(my_BH(p_value_2D_NPMLE_original, alpha))
```

### NPMLE with 1D projection

```{r}
lambda_projection_list_original = NPMLE_2D_result_original$grid[, 1] / NPMLE_2D_result_original$grid[, 2]
```

```{r}
p_value_1D_projection_original = P_value_1D_projection(information_original, lambda_projection_list_original, NPMLE_2D_result_original$mass)
```

```{r}
hist(p_value_1D_projection_original)
```

```{r}
length(my_BH(p_value_1D_projection_original, alpha))
```

### Welch

```{r}
p_value_Welch_original = P_value_Welch(information_original)
```

```{r}
hist(p_value_Welch_original)
```

```{r}
length(my_BH(p_value_Welch_original, alpha))
```

### Pooled_t_test

```{r}
p_value_t_original = P_value_pooled_t_test(information_original$m, Y_A, Y_B)
```

```{r}
hist(p_value_t_original)
```

```{r}
length(my_BH(p_value_t_original, alpha))
```

```{r}
dis_1D_original = my_BH(p_value_1D_NPMLE_original, alpha)
dis_2D_original = my_BH(p_value_2D_NPMLE_original, alpha)
dis_Welch_original = my_BH(p_value_Welch_original, alpha)
dis_t_original = my_BH(p_value_t_original, alpha)
```

```{r}
de_1D_original = rep(0, nrow(Y_A))
de_1D_original[dis_1D_original] = 1

de_2D_original = rep(0, nrow(Y_A))
de_2D_original[dis_2D_original] = 1

de_Welch_original = rep(0, nrow(Y_A))
de_Welch_original[dis_Welch_original] = 1

de_t_original = rep(0, nrow(Y_A))
de_t_original[dis_t_original] = 1
```

```{r}
df_de_original = cbind(de_1D_original, de_2D_original, de_Welch_original, de_t_original)
colnames(df_de_original) = c("1D_NPMLE", "2D_NPMLE", "Welch", "Pooled t-test")
vennDiagram(df_de_original, circle.col=c("blue","red","green","grey"))
```

## EPB with weight info based on voom

### w_A and w_B, Y_A and Y_B

```{r}
#w_A = w[, c(1,2,6,7,8,9,10)]
#w_B = w[, c(3,4,5)]

w_A = w[, c(1,2,3,4,8)]
w_B = w[, c(5,6,7)]

Y_A = Y1
Y_B = Y2
```

### extract sufficient statistics

```{r}
source('voom_EPB.R')
```

```{r}
information = information_extractor(Y_A, Y_B, w_A, w_B)
```

### NPMLE with 1D

```{r}
p_value_1D_NPMLE = P_value_1D_NPMLE(information, NPMLE_1D_parameter)
```

```{r}
hist(p_value_1D_NPMLE)
```

```{r}
length(my_BH(p_value_1D_NPMLE, alpha))
```

### NPMLE with 2D

```{r}
NPMLE_2D_result = NPMLE_2D(S1_list = information$S1_list, S2_list = information$S2_list, B1 = NPMLE_2D_parameter[1], B2 = NPMLE_2D_parameter[2], m = information$m, n1 = information$n1, n2 = information$n2, lower_quantile = NPMLE_2D_parameter[3], upper_quantile = NPMLE_2D_parameter[4])
```


```{r}
df_2D_weighted_voom = data.frame(x = NPMLE_2D_result$grid[, 1], y = NPMLE_2D_result$grid[, 2], prob = NPMLE_2D_result$mass)
```

```{r}
write.csv(df_2D_weighted_voom, '2D_weighted_voom_ModHC.csv')
```

```{r}
find_threshold = function(mass, Total_mass = 0.98) {
  sorted_mass = sort(mass, decreasing = TRUE)
  sum = 0
  for (i in c(1:length(mass))) {
    sum = sum + sorted_mass[i]
    if (sum >= Total_mass) {
      return (sorted_mass[i+1])
    }
  }
}
```

```{r, fig.width=12, fig.height=10}
Total_mass = 0.99
threshold_voom = find_threshold(df_2D_weighted_voom$prob, Total_mass = Total_mass)
size_breaks = exp(seq(log(min(df_2D_weighted_voom$prob[df_2D_weighted_voom$prob > threshold_voom])), log(max(df_2D_weighted_voom$prob)), length.out = 10))
plot_G_voom = ggplot(df_2D_weighted_voom, aes(x = log(x), y = log(y))) +
  geom_point(aes(size = ifelse(prob < threshold_voom, NA, prob)), color = "blue", alpha = 0.8) +
  scale_size_continuous(range = c(0.2, 5), breaks = size_breaks) +  # Adjust the range of point sizes
  theme_minimal() +
  labs(title = expression(paste(hat(G)({sigma[A]}^2, {sigma[B]}^2), ' based on Weights Estimated by Voom (Threshold = 0.99)')),
       x = expression(log({sigma[A]}^2)),
       y = expression(log({sigma[B]}^2))) +
  theme(plot.title = element_text(hjust = 0.5), legend.position = 'none')
plot_G_voom
```

```{r}
#ggsave(filename = 'G(var1, var2) with voom.jpg', plot = plot_G_voom, width = 12, height = 10, dpi = 500)
```

```{r}
p_value_2D_NPMLE = P_value_2D_NPMLE(information, NPMLE_2D_result$grid, NPMLE_2D_result$mass)
```

```{r}
hist(p_value_2D_NPMLE)
```

```{r}
length(my_BH(p_value_2D_NPMLE, alpha))
```


### NPMLE with 1D projection

```{r}
lambda_projection_list = NPMLE_2D_result$grid[, 1] / NPMLE_2D_result$grid[, 2]
```

```{r}
df_lambda = data.frame(x = lambda_projection_list, prob = NPMLE_2D_result$mass)
```

```{r, fig.width=8, fig.height=6}
plot_1D_voom = ggplot(df_lambda, aes(x = log(x), y = 0)) +
  geom_segment(aes(xend = log(x), yend = prob), size = 1, color = "blue") +
  scale_y_continuous(name = "Density", limits = c(0, max(df_lambda$prob))) +
  theme_minimal() +
  labs(title = expression(paste(hat(G)({sigma[A]}^2/{sigma[B]}^2), ' based on Weights estimated by Voom')),
       x = expression(log({sigma[A]}^2/{sigma[B]}^2))) +
  theme(plot.title = element_text(hjust = 0.5))
plot_1D_voom
```

```{r}
#ggsave(filename = 'G(lambda) by Voom.jpg', plot = plot_1D_voom, width = 8, height = 6, dpi = 500)
```

```{r}
df_lambda_with_ecdf = arrange(df_lambda, x) %>% mutate(ecdf = cumsum(prob))
```

```{r}
plot(log(df_lambda_with_ecdf$x), df_lambda_with_ecdf$ecdf, xlim = c(-2, 2), type = 'l', col = 'blue')
```

```{r}
p_value_1D_projection = P_value_1D_projection(information, lambda_projection_list, NPMLE_2D_result$mass)
```

```{r}
hist(p_value_1D_projection)
```

```{r}
length(my_BH(p_value_1D_projection, alpha))
```

### Welch

```{r}
p_value_Welch = P_value_Welch(information)
```

```{r}
hist(p_value_Welch)
```

```{r}
length(my_BH(p_value_Welch, alpha))
```

### Pooled t-test

```{r}
p_value_t = P_value_pooled_t_test(information)
```

```{r}
hist(p_value_t)
```

```{r}
length(my_BH(p_value_t, alpha))
```

### EV-NPMLE

```{r}
p_value_EV = P_value_EV_NPMLE(information, EV_NPMLE_1D_parameter)
```

```{r}
hist(p_value_EV)
```

```{r}
length(my_BH(p_value_EV, alpha))
```

```{r}
EV_NPMLE_1D = function(S1_list, S2_list, B, m, n1, n2, lower_quantile, upper_quantile) {
  
  S_list = c(S1_list, S2_list)
  
  lower = quantile(S_list, lower_quantile)
  upper = quantile(S_list, upper_quantile)
  log_u = seq(log(lower), log(upper), length = B)
  u = exp(log_u)
  d = rep(1,B)
  w = rep(1, m * 2) / (m * 2) 
  A1 = outer(S1_list, u, FUN = p_s_j_given_sigma2_EV, n = n1)
  A2 = outer(S2_list, u, FUN = p_s_j_given_sigma2_EV, n = n2)
  A = rbind(A1, A2)
  result = KWPrimal(A, d, w)
  mass = result$f/sum(result$f)
  
  output = list('grid' = u, 'mass' = mass)
}
```

```{r}
hat_F = EV_NPMLE_1D_F(information$S1_list, information$S2_list, EV_NPMLE_1D_parameter[1], information$m, information$n1, information$n2, EV_NPMLE_1D_parameter[2], EV_NPMLE_1D_parameter[3])
```

```{r}
df_1D_F_PBMC1 = data.frame(x = hat_F$grid, prob = hat_F$mass)
```

```{r}
write.csv(df_1D_F_PBMC1, '1D_F_PBMC_voom.csv')
```

## Visualization

```{r}
dis_1D = my_BH(p_value_1D_NPMLE, alpha)
dis_2D = my_BH(p_value_2D_NPMLE, alpha)
dis_Welch = my_BH(p_value_Welch, alpha)
dis_t = my_BH(p_value_t, alpha)
```

```{r}
de_1D = rep(0, nrow(Y_A))
de_1D[dis_1D] = 1

de_2D = rep(0, nrow(Y_A))
de_2D[dis_2D] = 1

de_Welch = rep(0, nrow(Y_A))
de_Welch[dis_Welch] = 1

de_t = rep(0, nrow(Y_A))
de_t[dis_t] = 1
```

```{r}
df_de = cbind(de_1D, de_2D, de_Welch, de_t)
colnames(df_de) = c("1D_NPMLE", "2D_NPMLE", "Welch", "Pooled t-test")
vennDiagram(df_de, circle.col=c("blue","red","green","grey"))
```

## EPB with weight info from voombygroup

### w_A and w_B, Y_A and Y_B

```{r}
w_vbg = vbg$weights
#w_A = w_vbg[, c(1,2,6,7,8,9,10)]
#w_B = w_vbg[, c(3,4,5)]

w_A = w_vbg[, c(1,2,3,4,8)]
w_B = w_vbg[, c(5,6,7)]

Y_A = Y1
Y_B = Y2
```

### extract sufficient statistics

```{r}
source('voom_EPB.R')
```

```{r}
information_vbg = information_extractor(Y_A, Y_B, w_A, w_B)
```

### NPMLE with 1D

```{r}
p_value_1D_NPMLE_vbg = P_value_1D_NPMLE(information_vbg, NPMLE_1D_parameter)
```

```{r}
hist(p_value_1D_NPMLE_vbg)
```

```{r}
length(my_BH(p_value_1D_NPMLE_vbg, alpha))
```

### NPMLE with 2D

```{r}
NPMLE_2D_result_vbg = NPMLE_2D(S1_list = information_vbg$S1_list, S2_list = information_vbg$S2_list, B1 = NPMLE_2D_parameter[1], B2 = NPMLE_2D_parameter[2], m = information_vbg$m, n1 = information_vbg$n1, n2 = information_vbg$n2, lower_quantile = NPMLE_2D_parameter[3], upper_quantile = NPMLE_2D_parameter[4])
```

```{r}
df_2D_weighted_vbg = data.frame(x = NPMLE_2D_result_vbg$grid[, 1], y = NPMLE_2D_result_vbg$grid[, 2], prob = NPMLE_2D_result_vbg$mass)
```

```{r}
write.csv(df_2D_weighted_vbg, '2D_weighted_vbg_ModHC.csv')
```

```{r, fig.width = 12, flg.height = 10}
Total_mass = 0.99
threshold_vbg = find_threshold(df_2D_weighted_vbg$prob, Total_mass = Total_mass)
size_breaks = exp(seq(log(min(df_2D_weighted_vbg$prob[df_2D_weighted_vbg$prob > threshold_vbg])), log(max(df_2D_weighted_vbg$prob)), length.out = 20))
plot_G_vbg = ggplot(df_2D_weighted_vbg, aes(x = log(x), y = log(y))) +
  geom_point(aes(size = ifelse(prob < threshold_vbg, NA, prob)), color = "blue", alpha = 0.8) +
  scale_size_continuous(range = c(0.2, 5), breaks = size_breaks) +  # Adjust the range of point sizes
  theme_minimal() +
  labs(title = expression(paste(hat(G)({sigma[A]}^2, {sigma[B]}^2), ' based on Weights estimated by VoombyGroup (Threshold = 0.99)')),
       x = expression(log({sigma[A]}^2)),
       y = expression(log({sigma[B]}^2))) +
  theme(plot.title = element_text(hjust = 0.5), legend.position = 'none')
plot_G_vbg
```

```{r}
#ggsave(filename = 'G(var1, var2) with VoombyGroup.jpg', plot = plot_G_vbg, width = 12, height = 10, dpi = 500)
```

```{r}
p_value_2D_NPMLE_vbg = P_value_2D_NPMLE(information_vbg, NPMLE_2D_result_vbg$grid, NPMLE_2D_result_vbg$mass)
```

```{r}
hist(p_value_2D_NPMLE_vbg)
```

```{r}
length(my_BH(p_value_2D_NPMLE_vbg, alpha))
```


### NPMLE with 1D projection

```{r}
lambda_projection_list_vbg = NPMLE_2D_result_vbg$grid[, 1] / NPMLE_2D_result_vbg$grid[, 2]
```

```{r}
df_lambda_vbg = data.frame(x = lambda_projection_list_vbg, prob = NPMLE_2D_result_vbg$mass)
```

```{r}
df_lambda_with_ecdf_vbg = arrange(df_lambda_vbg, x) %>% mutate(ecdf = cumsum(prob))
```

```{r}
plot(log(df_lambda_with_ecdf$x), df_lambda_with_ecdf$ecdf, xlim = c(-2, 2), lwd = 1, type = 'l', col = 'blue')
lines(log(df_lambda_with_ecdf_vbg$x), df_lambda_with_ecdf_vbg$ecdf, col = 'black')
```

```{r, fig.width=8, fig.height=6}
plot_1D_vbg = ggplot(df_lambda_vbg, aes(x = log(x), y = 0)) +
  geom_segment(aes(xend = log(x), yend = prob), size = 1, color = "blue") +
  scale_y_continuous(name = "Density", limits = c(0, max(df_lambda_vbg$prob))) +
  theme_minimal() +
  labs(title = expression(paste(hat(G)({sigma[A]}^2/{sigma[B]}^2), ' based on Weights estimated by VoombyGroup')),
       x = expression(log({sigma[A]}^2/{sigma[B]}^2))) +
  theme(plot.title = element_text(hjust = 0.5))
plot_1D_vbg
```
```{r}
#ggsave(filename = 'G(lambda) by VoombyGroup.jpg', plot = plot_1D_vbg, width = 8, height = 6, dpi = 500)
```

```{r}
p_value_1D_projection_vbg = P_value_1D_projection(information_vbg, lambda_projection_list_vbg, NPMLE_2D_result_vbg$mass)
```

```{r}
hist(p_value_1D_projection_vbg)
```

```{r}
length(my_BH(p_value_1D_projection_vbg, alpha))
```

### Welch

```{r}
p_value_Welch_vbg = P_value_Welch(information_vbg)
```

```{r}
hist(p_value_Welch_vbg)
```

```{r}
length(my_BH(p_value_Welch_vbg, alpha))
```

### Pooled t-test

```{r}
p_value_t_vbg = P_value_pooled_t_test(information_vbg)
```

```{r}
hist(p_value_t_vbg)
```

```{r}
length(my_BH(p_value_t_vbg, alpha))
```

### EV-NPMLE

```{r}
p_value_EV_vbg = P_value_EV_NPMLE(information_vbg, EV_NPMLE_1D_parameter)
```

```{r}
hist(p_value_EV_vbg)
```

```{r}
length(my_BH(p_value_EV_vbg, alpha))
```

```{r}
hat_F_vbg = EV_NPMLE_1D_F(information_vbg$S1_list, information_vbg$S2_list, EV_NPMLE_1D_parameter[1], information_vbg$m, information_vbg$n1, information_vbg$n2, EV_NPMLE_1D_parameter[2], EV_NPMLE_1D_parameter[3])
```

```{r}
df_1D_F_PBMC1_vbg = data.frame(x = hat_F_vbg$grid, prob = hat_F_vbg$mass)
```

```{r}
write.csv(df_1D_F_PBMC1_vbg, '1D_F_PBMC1_vbg_ModHC.csv')
```

### Visualizaition

```{r}
dis_1D_vbg = my_BH(p_value_1D_NPMLE_vbg, alpha)
dis_2D_vbg = my_BH(p_value_2D_NPMLE_vbg, alpha)
dis_Welch_vbg = my_BH(p_value_Welch_vbg, alpha)
dis_t_vbg = my_BH(p_value_t_vbg, alpha)
```

```{r}
de_1D_vbg = rep(0, nrow(Y_A))
de_1D_vbg[dis_1D_vbg] = 1

de_2D_vbg = rep(0, nrow(Y_A))
de_2D_vbg[dis_2D_vbg] = 1

de_Welch_vbg = rep(0, nrow(Y_A))
de_Welch_vbg[dis_Welch_vbg] = 1

de_t_vbg = rep(0, nrow(Y_A))
de_t_vbg[dis_t_vbg] = 1
```

```{r}
df_de_vbg = cbind(de_1D_vbg, de_2D_vbg, de_Welch_vbg, de_t_vbg)
colnames(df_de_vbg) = c("1D_NPMLE", "2D_NPMLE", "Welch", "Pooled t-test")
vennDiagram(df_de_vbg, circle.col=c("blue","red","green","grey"))
```

## voom

```{r}
v = voom(y, design = design, plot = TRUE)
```

## voomWithQualityWeights without block design

```{r}
vvqw = voomWithQualityWeights(y, design = design, plot = TRUE)
```

## voomWithQualityWeights with block design

```{r}
vvqw_block = voomWithQualityWeights(y, design = design, var.group= group_assignment, plot = TRUE)
```

## voomByGroup

```{r}
vbg = voomByGroup(y, design = design, group = group_assignment, plot = 'combine')
```


## Differential expression analysis

### based on my voom

```{r}
contr.matrix <- makeContrasts(
  AvsH = group_assignmentModerate- group_assignmentHC,
  levels = colnames(design))
contr.matrix
```

#### focus on row 1

fit weighted linear model with lmFit

```{r}
fit <- lmFit(v, design)
fit$coefficients[1, ]
```

fit weighted linear model with lm

```{r}
Y_r1 = Y[1, ]
X = design
Dg_r1 = diag(w[1, ])
```

```{r}
w_lm_r1 = lm(Y_r1 ~ 0 + X, weights = w[1,])
w_lm_r1$coefficients
w_lm_r1$df.residual
```

directly solve weighted linear model

```{r}
solve(t(X) %*% Dg_r1 %*% X) %*% t(X) %*% Dg_r1 %*% Y_r1
```

transform Y and X and solve weighted linear model

```{r}
Dg_half = Dg_r1^(1/2)
Y_new = Dg_half %*% Y_r1
X_new = Dg_half %*% X
solve(t(X_new) %*% X_new) %*% t(X_new) %*% Y_new
lm_new = lm(Y_new ~ 0 + X_new)
sqrt(sum((lm_new$fitted.values - Y_new)^2) / 8)
```


```{r}
length(fit$sigma)
dim(Y_hat)
fit$sigma[1]
sqrt(sum((w_lm_r1$model$`v$E[1, ]` - w_lm_r1$fitted.values)^2) / 9)
```


```{r}
#fit
vfit = contrasts.fit(fit, contrasts=contr.matrix)
#vfit$coefficients
#fit$coefficients %*% contr.matrix
```

```{r}
tfit = treat(vfit, lfc=0)
```

```{r}
length(my_BH(tfit$p.value, alpha))
hist(tfit$p.value)
```



```{r}
find_de <- function(y, design, contr.matrix) {
 fit <- lmFit(y, design)
 vfit <- contrasts.fit(fit, contrasts=contr.matrix)
 tfit <- treat(vfit, lfc=0)
 decideTests(tfit) -> de
 return(de)
}
```

```{r,message=FALSE, warning=FALSE}
fit = lmFit(v, design)
vfit = contrasts.fit(fit, contrasts=contr.matrix)
tfit = treat(vfit, lfc=0)
```

```{r}
length(my_BH(tfit$p.value, alpha))
```

```{r,message=FALSE, warning=FALSE}
fit = lmFit(vvqw, design)
vfit = contrasts.fit(fit, contrasts=contr.matrix)
tfit = treat(vfit, lfc=0)
```

```{r}
length(my_BH(tfit$p.value, alpha))
```

```{r,message=FALSE, warning=FALSE}
fit = lmFit(vvqw_block, design)
vfit = contrasts.fit(fit, contrasts=contr.matrix)
tfit = treat(vfit, lfc=0)
```

```{r}
length(my_BH(tfit$p.value, alpha))
```

```{r,message=FALSE, warning=FALSE}
fit = lmFit(vbg, design)
vfit = contrasts.fit(fit, contrasts=contr.matrix)
tfit = treat(vfit, lfc=0)
```

```{r}
length(my_BH(tfit$p.value, alpha))
```

```{r}
de_v[, 1]
```


```{r}
cbind(de_v[, 1],de_vvqw[,1],de_vvqw_block[,1],de_vbg[,1]) -> df
colnames(df) <- c("voom","voomQW","voomQWB","voomByGroup")
vennDiagram(df, circle.col=c("blue","red","green","grey"))
```


