---
title: "Rejection Region"
output: pdf_document
date: "2024-11-09"
---

```{r}
library(limma)
library(edgeR)
source('voomByGroup.R')
library(ggplot2)
library(tidyverse)
```

# load PBMC1 data

```{r}
counts = readRDS("./PBMC1/counts.rds")
group = readRDS("./PBMC1/group_id.rds")
```

```{r}
source('voom_EPB.R')
source('helper pool.R')
```

```{r}
group
```

# Data Filtering

```{r}
high_expression_counts = counts[rowSums(counts)>50,]
```

```{r}
filter = (group == 'Moderate' | group == 'HC')
```

```{r}
filtered_counts = high_expression_counts[, filter]
filtered_group = group[filter]
```

# Create DGElist

```{r}
y = DGEList(filtered_counts)
```

```{r}
y$samples$group
y$samples$group = filtered_group
y$samples$group
```

# Calculate Normalizing Factors

```{r}
y = calcNormFactors(y)
```

```{r}
y$samples
```
# Create the design matrix based on group information.

```{r}
group_assignment = y$samples$group
design = model.matrix(~0 + group_assignment)
design
```

## Normalize library size R

```{r}
R = y$samples$lib.size * y$samples$norm.factors
```

## Calculate log-cpm

```{r}
Y = t(log2((t(filtered_counts) + 0.5)/(R+1) * 1e6))
```

## Normalize log-cpm

```{r}
Y = normalizeBetweenArrays(Y, method='none')
```

## voom

```{r}
v = voom(y, design = design, plot = TRUE)
```

## voomByGroup

```{r}
vbg = voomByGroup(y, design = design, group = group_assignment, plot = 'combine')
```

# Rejection region voom

```{r}
Y1 = Y[, c(1,2,3,4,8)]
Y2 = Y[, c(5,6,7)]

w = v$weights
w1 = w[, c(1,2,3,4,8)]
w2 = w[, c(5,6,7)]
```

Samples for test

```{r}
Y1_1 = Y1[1, ]
Y2_1 = Y2[1, ]
K1 = length(Y1_1)
K2 = length(Y2_1)
n1 = sum(w1[1,])
n2 = sum(w2[1,])
m1 = mean(Y1_1)
m2 = mean(Y2_1)
sd1 = sqrt(var(Y1_1))
sd2 = sqrt(var(Y2_1))
se = sqrt((1/n1 + 1/n2) * ((K1-1) * sd1^2 + (K2-1) * sd2^2)/(K1+K2-2))
md = m1 - m2
t = md / se
t
```

```{r}
info = information_extractor(Y1, Y2, w1, w2)
```


```{r}
tau_list = info$S1_list/info$S2_list

log_tau_list = log(tau_list)

range = quantile(log_tau_list, c(0.025, 1-0.025))

range_filter = log(tau_list) >= range[1] & log(tau_list) <= range[2]

log_tau_list = log_tau_list[range_filter]

hist(log_tau_list, breaks = 40)

tau_grid = exp(seq(min(log_tau_list), max(log_tau_list), length.out = 1000))
```

Range of sample t_BF to determine range of root solver

```{r}
t_pool_list = c()
D = c()
for (i in 1:nrow(Y1)) {
  m1_i = mean(Y1[i, ])
  m2_i = mean(Y2[i, ])
  s1_i = var(Y1[i, ])
  s2_i = var(Y2[i, ])
  w1_i = w1[i, ]
  w2_i = w2[i, ]
  n1 = sum(w1_i)
  n2 = sum(w2_i)
  t_pool_i = (m1_i - m2_i) / sqrt((1/n1 + 1/n2) * ((K1-1) * s1_i + (K2-1) * s2_i)/(K1+K2-2))
  t_pool_list = c(t_pool_list, t_pool_i)
  Di = s1_i/n1 + s2_i/n2
  D = c(D, Di)
}
t_pool_list[1]

max(t_pool_list)
D = D[range_filter]

t_pool_list = t_pool_list[range_filter]
```

```{r}
result_csv = read.csv('./Mod vs HC/2D_weighted_vbg_ModHC.csv')
```

```{r}
grid = result_csv[, 2:3]
mass = result_csv[, 4]
```

```{r}
#target = sort(abs(log_tau_list), decreasing = TRUE)[1:50]

#sort(D[abs(log_tau_list) %in% target] / median(D))

#cbind(info$S1_list[log(tau_list) >= -5][abs(log_tau_list) %in% target], info$S2_list[log(tau_list) >= -5][abs(log_tau_list) %in% target], D[abs(log_tau_list) %in% target] / median(D))
```


```{r}
cutoff_1DNPMLE = 0.0026508907
cutoff_2DNPMLE = 0.0030585356
cutoff_Welch = 0.0002270525
cutoff_pooled_t = 0.0038435845
cutoff_B_F = -Inf
cutoff_EV_NPMLE = 0.0035106845
```

```{r}
grid_1D = grid_2D[, 1] / grid_2D[, 2]
```

# Beherens-Fisher test

```{r}
t_BF_005 = c()

for (tau in tau_grid) {
  t_BF_005_i = pool_pvalue_BF_solver_positive(tau, K1, K2, w1[1, ], w2[1, ], 0.05)
  t_BF_005 = append(t_BF_005, t_BF_005_i)
}
```

```{r}
t_BF_bh = c()

for (tau in tau_grid) {
  t_BF_bh_i = pool_pvalue_BF_solver_positive(tau, K1, K2, 0.1)
  t_BF_bh = append(t_BF_bh, t_BF_bh_i)
}
```

# 1DNPMLE

```{r}
p_value_npmle_j(K1, K2, m1, m2, sd1^2, sd2^2, w1[1,], w2[1,],grid_1D, mass, sd1^2/sd2^2)
pool_pvalue_1DNPMLE(t, K1, K2, w1[1, ], w2[1, ], grid_1D, mass, sd1^2/sd2^2)
pool_pvalue_1DNPMLE_solver_positive(K1, K2, w1[1, ], w2[1, ], grid_1D, mass, sd1^2/sd2^2, 0.05)
```

```{r}
t_1DNPMLE_005 = c()
#t_1DNPMLE_bh = c()

for (tau in tau_grid) {
  t_1DNPMLE_005_i = pool_pvalue_1DNPMLE_solver_positive(K1, K2, w1[1, ], w2[1, ], grid_1D, mass, tau, 0.05)
  #t_1DNPMLE_bh_i = BF_pvalue_1DNPMLE_solver_positive(K1, K2, grid_1D, mass, tau, cutoff_1DNPMLE)
  t_1DNPMLE_005 = append(t_1DNPMLE_005, t_1DNPMLE_005_i)
  #t_1DNPMLE_bh = append(t_1DNPMLE_bh, t_1DNPMLE_bh_i)
}
```

# Welch

```{r}
Welch_approximation_p(K1, K2, m1, m2, sd1^2, sd2^2, w1[1, ], w2[1, ])
pool_pvalue_Welch(t, sd1^2/sd2^2, K1, K2, w1[1, ], w2[1, ])
pool_pvalue_Welch_solver_positive(sd1^2/sd2^2, K1, K2, w1[1, ], w2[1, ], 0.05)
t
```

```{r}
t_Welch_005 = c()
#t_Welch_bh = c()

for (tau in tau_grid) {
  t_Welch_005_i = pool_pvalue_Welch_solver_positive(tau, K1, K2, w1[1, ], w2[1, ], 0.05)
  #t_Welch_bh_i = BF_pvalue_Welch_solver_positive(tau, K1, K2, cutoff_Welch)
  t_Welch_005 = append(t_Welch_005, t_Welch_005_i)
  #t_Welch_bh = append(t_Welch_bh, t_Welch_bh_i)
}
```

# Pooled t-test

```{r}
pooled_t_test_p(K1, K2, m1, m2, sd1^2, sd2^2, w1[1, ], w2[1, ])
pool_pvalue_t(t, sd1^2/sd2^2, K1, K2, w1[1, ], w2[1, ])
pool_pvalue_t_solver_positive(sd1^2/sd2^2, K1, K2, w1[1, ], w2[1, ], 0.05)
t
```

```{r}
t_t_005 = c()
#t_t_bh = c()

for (tau in tau_grid) {
  t_t_005_i = pool_pvalue_t_solver_positive(tau, K1, K2, w1[1, ], w2[1, ], 0.05)
  #t_t_bh_i = BF_pvalue_t_solver_positive(tau, K1, K2, cutoff_pooled_t)
  t_t_005 = append(t_t_005, t_t_005_i)
  #t_t_bh = append(t_t_bh, t_t_bh_i)
}
```

# Visualization

```{r}
plot_2D = function(u1,u2) {
  ggplot(data.frame(u1 = u1, u2 = u2), aes(x = u1, y = u2)) +
    stat_bin2d(bins = 200) +
    scale_fill_gradient(low = "lightblue", high = "darkblue") +
    labs(x = "u1", y = "u2", fill = "Count") +
    scale_y_continuous(limits = c(-30, 30)) +
    theme_minimal()
}
```

```{r}
plot_2D(log_tau_list, t_BF_list) + 
  
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = t_BF_005), aes(x = log_tau_grid, y = y, color = 'BF (unadj.)'), linetype = 'dashed') +
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = -t_BF_005), aes(x = log_tau_grid, y = y, color = 'BF (unadj.)'), linetype = 'dashed') +
  
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = t_1DNPMLE_005), aes(x = log_tau_grid, y = y, color = '1D-NPMLE (unadj.)'), linetype = 'dashed') +
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = -t_1DNPMLE_005), aes(x = log_tau_grid, y = y, color = '1D-NPMLE (unadj.)'), linetype = 'dashed') +
  
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = t_Welch_005), aes(x = log_tau_grid, y = y, color = 'Welch (unadj.)'), linetype = 'dashed') +
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = -t_Welch_005), aes(x = log_tau_grid, y = y, color = 'Welch (unadj.)'), linetype = 'dashed') +
  
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = t_t_005), aes(x = log_tau_grid, y = y, color = 'Pooled t (unadj.)'), linetype = 'dashed') +
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = -t_t_005), aes(x = log_tau_grid, y = y, color = 'Pooled t (unadj.)'), linetype = 'dashed') +
  
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = t_BF_bh), aes(x = log_tau_grid, y = y, color = 'BF (BH)')) +
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = -t_BF_bh), aes(x = log_tau_grid, y = y, color = 'BF (BH)')) +
  
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = t_1DNPMLE_bh), aes(x = log_tau_grid, y = y, color = '1D-NPMLE (BH)')) +
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = -t_1DNPMLE_bh), aes(x = log_tau_grid, y = y, color = '1D-NPMLE (BH)')) +
  
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = t_Welch_bh), aes(x = log_tau_grid, y = y, color = 'Welch (BH)')) +
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = -t_Welch_bh), aes(x = log_tau_grid, y = y, color = 'Welch (BH)')) +
  
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = t_t_bh), aes(x = log_tau_grid, y = y, color = 'Pooled t (BH)')) +
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = -t_t_bh), aes(x = log_tau_grid, y = y, color = 'Pooled t (BH)')) +
  
  scale_color_manual(name = '', values = c('1D-NPMLE (BH)' = 'blue', 'BF (BH)' = 'pink', 'Welch (BH)' = 'green', 'Pooled t (BH)' = 'red', '1D-NPMLE (unadj.)' = 'blue', 'BF (unadj.)' = 'pink', 'Welch (unadj.)' = 'green', 'Pooled t (unadj.)' = 'red')) + 
  labs(x = expression(hat(lambda[i])), y = expression(T[i]^{BF})) + theme_minimal()
```

```{r}
plot_2D(log_tau_list, t_pool_list) + 
  
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = t_BF_005), aes(x = log_tau_grid, y = y, color = 'BF (unadj.)'), linetype = 'dashed') +
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = -t_BF_005), aes(x = log_tau_grid, y = y, color = 'BF (unadj.)'), linetype = 'dashed') +
  
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = t_1DNPMLE_005), aes(x = log_tau_grid, y = y, color = '1D-NPMLE (unadj.)'), linetype = 'dashed') +
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = -t_1DNPMLE_005), aes(x = log_tau_grid, y = y, color = '1D-NPMLE (unadj.)'), linetype = 'dashed') +
  
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = t_Welch_005), aes(x = log_tau_grid, y = y, color = 'Welch (unadj.)'), linetype = 'dashed') +
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = -t_Welch_005), aes(x = log_tau_grid, y = y, color = 'Welch (unadj.)'), linetype = 'dashed') +
  
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = t_t_005), aes(x = log_tau_grid, y = y, color = 'Pooled t (unadj.)'), linetype = 'dashed') +
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = -t_t_005), aes(x = log_tau_grid, y = y, color = 'Pooled t (unadj.)'), linetype = 'dashed') +
  
  scale_color_manual(name = '', values = c('1D-NPMLE (unadj.)' = 'blue', 'BF (unadj.)' = 'pink', 'Welch (unadj.)' = 'green', 'Pooled t (unadj.)' = 'red')) + 
  labs(x = expression(hat(lambda[i])), y = expression(T[i]^{BF})) + theme_minimal()
```

```{r}
par(mar = c(5, 4, 4, 8))

plot(log(tau_grid), t_BF_005, type = 'l', ylim = c(-30, 30), lwd = 2, col = 'pink', xlab = expression(hat(lambda[i])), ylab = expression(T[i]^{BF}), lty=2)
lines(log(tau_grid), -t_BF_005, lwd = 2, col = 'pink', lty=2)
#lines(log(tau_grid), t_BF_bh, lwd = 2, col = 'pink')
#lines(log(tau_grid), -t_BF_bh, lwd = 2, col = 'pink')

lines(log(tau_grid), t_1DNPMLE_005, lwd = 2, col = 'blue', lty=2)
lines(log(tau_grid), -t_1DNPMLE_005, lwd = 2, col = 'blue', lty=2)
#lines(log(tau_grid), t_1DNPMLE_bh, lwd = 2, col = 'blue')
#lines(log(tau_grid), -t_1DNPMLE_bh, lwd = 2, col = 'blue')

lines(log(tau_grid), t_Welch_005, lwd = 2, col = 'green', lty=2)
lines(log(tau_grid), -t_Welch_005, lwd = 2, col = 'green', lty=2)
#lines(log(tau_grid), t_Welch_bh, lwd = 2, col = 'green')
#lines(log(tau_grid), -t_Welch_bh, lwd = 2, col = 'green')

lines(log(tau_grid), t_t_005, lwd = 2, col = 'red', lty=2)
lines(log(tau_grid), -t_t_005, lwd = 2, col = 'red', lty=2)
#lines(log(tau_grid), t_t_bh, lwd = 2, col = 'red')
#lines(log(tau_grid), -t_t_bh, lwd = 2, col = 'red')

#legend('topright', c('1D_NPMLE (BH)', 'Welch (BH)', 'B_F (BH)', 'Pooled_t (BH)', '1D_NPMLE (unadj.)', 'Welch (unadj.)', 'B_F (unadj.)', 'Pooled_t (unadj.)'), col=c('blue', 'green', 'pink', 'red', 'blue', 'green', 'pink', 'red'), lwd=2, lty = c(1,1,1,1,2,2,2,2), cex = 0.7, inset = c(-0.32, 0), xpd = TRUE)
legend('topright', c('1D_NPMLE (unadj.)', 'Welch (unadj.)', 'B_F (unadj.)', 'Pooled_t (unadj.)'), col=c('blue', 'green', 'pink', 'red'), lwd=2, lty = c(2,2,2,2), cex = 0.7, inset = c(-0.32, 0), xpd = TRUE)
```

# Rejection region voombyGroup

```{r}
Y1 = Y[, c(1,2,3,4,8)]
Y2 = Y[, c(5,6,7)]

w = vbg$weights
w1 = w[, c(1,2,3,4,8)]
w2 = w[, c(5,6,7)]
```

Samples for test

```{r}
Y1_1 = Y1[1, ]
Y2_1 = Y2[1, ]
K1 = length(Y1_1)
K2 = length(Y2_1)
n1 = sum(w1[1,])
n2 = sum(w2[1,])
m1 = mean(Y1_1)
m2 = mean(Y2_1)
sd1 = sqrt(var(Y1_1))
sd2 = sqrt(var(Y2_1))
se = sqrt(sd1^2/n1 + sd2^2/n2)
md = m1 - m2
t = md / se
t
```

```{r}
info = information_extractor(Y1, Y2, w1, w2)
```


```{r}
tau_list = info$S1_list/info$S2_list

log_tau_list = log(tau_list)

range = quantile(log_tau_list, c(0.025, 1-0.025))

range_filter = log(tau_list) >= range[1] & log(tau_list) <= range[2]

log_tau_list = log_tau_list[range_filter]

hist(log_tau_list, breaks = 40)

tau_grid = exp(seq(min(log_tau_list), max(log_tau_list), length.out = 1000))
```

Range of sample t_BF to determine range of root solver

```{r}
t_BF_list = c()
D = c()
for (i in 1:nrow(Y1)) {
  m1_i = mean(Y1[i, ])
  m2_i = mean(Y2[i, ])
  s1_i = var(Y1[i, ])
  s2_i = var(Y2[i, ])
  w1_i = w1[i, ]
  w2_i = w2[i, ]
  n1 = sum(w1_i)
  n2 = sum(w2_i)
  t_BF_i = (m1_i - m2_i) / sqrt(s1_i/n1 + s2_i/n2)
  t_BF_list = c(t_BF_list, t_BF_i)
  Di = s1_i/n1 + s2_i/n2
  D = c(D, Di)
}
t_BF_list[1]

max(t_BF_list)
D = D[range_filter]

t_BF_list = t_BF_list[range_filter]
```

```{r}
result_csv = read.csv('./Mod vs HC/2D_weighted_vbg_ModHC.csv')
```

```{r}
grid = result_csv[, 2:3]
mass = result_csv[, 4]
```

```{r}
#target = sort(abs(log_tau_list), decreasing = TRUE)[1:50]

#sort(D[abs(log_tau_list) %in% target] / median(D))

#cbind(info$S1_list[log(tau_list) >= -5][abs(log_tau_list) %in% target], info$S2_list[log(tau_list) >= -5][abs(log_tau_list) %in% target], D[abs(log_tau_list) %in% target] / median(D))
```


```{r}
cutoff_1DNPMLE = 0.0026508907
cutoff_2DNPMLE = 0.0030585356
cutoff_Welch = 0.0002270525
cutoff_pooled_t = 0.0038435845
cutoff_B_F = -Inf
cutoff_EV_NPMLE = 0.0035106845
```

```{r}
grid_1D = grid_2D[, 1] / grid_2D[, 2]
```

# Beherens-Fisher test

```{r}
t_BF_005 = c()

for (tau in tau_grid) {
  t_BF_005_i = BF_pvalue_BF_solver_positive(tau, K1, K2, w1[1, ], w2[1, ], 0.05)
  t_BF_005 = append(t_BF_005, t_BF_005_i)
}
```

```{r}
t_BF_bh = c()

for (tau in tau_grid) {
  t_BF_bh_i = BF_pvalue_BF_solver_positive(tau, K1, K2, 0.1)
  t_BF_bh = append(t_BF_bh, t_BF_bh_i)
}
```

# 1DNPMLE

```{r}
p_value_npmle_j(K1, K2, m1, m2, sd1^2, sd2^2, w1[1,], w2[1,],grid_1D, mass, sd1^2/sd2^2)
BF_pvalue_1DNPMLE(t, K1, K2, w1[1, ], w2[1, ], grid_1D, mass, sd1^2/sd2^2)
BF_pvalue_1DNPMLE_solver_positive(K1, K2, w1[1, ], w2[1, ], grid_1D, mass, sd1^2/sd2^2, 0.05)
```

```{r}
t_1DNPMLE_005 = c()
#t_1DNPMLE_bh = c()

for (tau in tau_grid) {
  t_1DNPMLE_005_i = BF_pvalue_1DNPMLE_solver_positive(K1, K2, w1[1, ], w2[1, ], grid_1D, mass, tau, 0.05)
  #t_1DNPMLE_bh_i = BF_pvalue_1DNPMLE_solver_positive(K1, K2, grid_1D, mass, tau, cutoff_1DNPMLE)
  t_1DNPMLE_005 = append(t_1DNPMLE_005, t_1DNPMLE_005_i)
  #t_1DNPMLE_bh = append(t_1DNPMLE_bh, t_1DNPMLE_bh_i)
}
```

# Welch

```{r}
Welch_approximation_p(K1, K2, m1, m2, sd1^2, sd2^2, w1[1, ], w2[1, ])
BF_pvalue_Welch(t, sd1^2/sd2^2, K1, K2, w1[1, ], w2[1, ])
BF_pvalue_Welch_solver_positive(sd1^2/sd2^2, K1, K2, w1[1, ], w2[1, ], 0.05)
t
```

```{r}
t_Welch_005 = c()
#t_Welch_bh = c()

for (tau in tau_grid) {
  t_Welch_005_i = BF_pvalue_Welch_solver_positive(tau, K1, K2, w1[1, ], w2[1, ], 0.05)
  #t_Welch_bh_i = BF_pvalue_Welch_solver_positive(tau, K1, K2, cutoff_Welch)
  t_Welch_005 = append(t_Welch_005, t_Welch_005_i)
  #t_Welch_bh = append(t_Welch_bh, t_Welch_bh_i)
}
```

# Pooled t-test

```{r}
pooled_t_test_p(K1, K2, m1, m2, sd1^2, sd2^2, w1[1, ], w2[1, ])
BF_pvalue_t(t, sd1^2/sd2^2, K1, K2, w1[1, ], w2[1, ])
BF_pvalue_t_solver_positive(sd1^2/sd2^2, K1, K2, w1[1, ], w2[1, ], 0.05)
t
```

```{r}
t_t_005 = c()
#t_t_bh = c()

for (tau in tau_grid) {
  t_t_005_i = BF_pvalue_t_solver_positive(tau, K1, K2, w1[1, ], w2[1, ], 0.05)
  #t_t_bh_i = BF_pvalue_t_solver_positive(tau, K1, K2, cutoff_pooled_t)
  t_t_005 = append(t_t_005, t_t_005_i)
  #t_t_bh = append(t_t_bh, t_t_bh_i)
}
```

# Visualization

```{r}
plot_2D = function(u1,u2) {
  ggplot(data.frame(u1 = u1, u2 = u2), aes(x = u1, y = u2)) +
    stat_bin2d(bins = 200) +
    scale_fill_gradient(low = "lightblue", high = "darkblue") +
    labs(x = "u1", y = "u2", fill = "Count") +
    scale_y_continuous(limits = c(-20, 20)) +
    theme_minimal()
}
```

```{r}
plot_2D(log_tau_list, t_BF_list) + 
  
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = t_BF_005), aes(x = log_tau_grid, y = y, color = 'BF (unadj.)'), linetype = 'dashed') +
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = -t_BF_005), aes(x = log_tau_grid, y = y, color = 'BF (unadj.)'), linetype = 'dashed') +
  
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = t_1DNPMLE_005), aes(x = log_tau_grid, y = y, color = '1D-NPMLE (unadj.)'), linetype = 'dashed') +
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = -t_1DNPMLE_005), aes(x = log_tau_grid, y = y, color = '1D-NPMLE (unadj.)'), linetype = 'dashed') +
  
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = t_Welch_005), aes(x = log_tau_grid, y = y, color = 'Welch (unadj.)'), linetype = 'dashed') +
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = -t_Welch_005), aes(x = log_tau_grid, y = y, color = 'Welch (unadj.)'), linetype = 'dashed') +
  
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = t_t_005), aes(x = log_tau_grid, y = y, color = 'Pooled t (unadj.)'), linetype = 'dashed') +
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = -t_t_005), aes(x = log_tau_grid, y = y, color = 'Pooled t (unadj.)'), linetype = 'dashed') +
  
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = t_BF_bh), aes(x = log_tau_grid, y = y, color = 'BF (BH)')) +
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = -t_BF_bh), aes(x = log_tau_grid, y = y, color = 'BF (BH)')) +
  
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = t_1DNPMLE_bh), aes(x = log_tau_grid, y = y, color = '1D-NPMLE (BH)')) +
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = -t_1DNPMLE_bh), aes(x = log_tau_grid, y = y, color = '1D-NPMLE (BH)')) +
  
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = t_Welch_bh), aes(x = log_tau_grid, y = y, color = 'Welch (BH)')) +
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = -t_Welch_bh), aes(x = log_tau_grid, y = y, color = 'Welch (BH)')) +
  
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = t_t_bh), aes(x = log_tau_grid, y = y, color = 'Pooled t (BH)')) +
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = -t_t_bh), aes(x = log_tau_grid, y = y, color = 'Pooled t (BH)')) +
  
  scale_color_manual(name = '', values = c('1D-NPMLE (BH)' = 'blue', 'BF (BH)' = 'pink', 'Welch (BH)' = 'green', 'Pooled t (BH)' = 'red', '1D-NPMLE (unadj.)' = 'blue', 'BF (unadj.)' = 'pink', 'Welch (unadj.)' = 'green', 'Pooled t (unadj.)' = 'red')) + 
  labs(x = expression(hat(lambda[i])), y = expression(T[i]^{BF})) + theme_minimal()
```

```{r}
plot_2D(log_tau_list, t_BF_list) + 
  
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = t_BF_005), aes(x = log_tau_grid, y = y, color = 'BF (unadj.)'), linetype = 'dashed') +
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = -t_BF_005), aes(x = log_tau_grid, y = y, color = 'BF (unadj.)'), linetype = 'dashed') +
  
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = t_1DNPMLE_005), aes(x = log_tau_grid, y = y, color = '1D-NPMLE (unadj.)'), linetype = 'dashed') +
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = -t_1DNPMLE_005), aes(x = log_tau_grid, y = y, color = '1D-NPMLE (unadj.)'), linetype = 'dashed') +
  
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = t_Welch_005), aes(x = log_tau_grid, y = y, color = 'Welch (unadj.)'), linetype = 'dashed') +
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = -t_Welch_005), aes(x = log_tau_grid, y = y, color = 'Welch (unadj.)'), linetype = 'dashed') +
  
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = t_t_005), aes(x = log_tau_grid, y = y, color = 'Pooled t (unadj.)'), linetype = 'dashed') +
  geom_line(data = data.frame(log_tau_grid = log(tau_grid), y = -t_t_005), aes(x = log_tau_grid, y = y, color = 'Pooled t (unadj.)'), linetype = 'dashed') +
  
  scale_color_manual(name = '', values = c('1D-NPMLE (unadj.)' = 'blue', 'BF (unadj.)' = 'pink', 'Welch (unadj.)' = 'green', 'Pooled t (unadj.)' = 'red')) + 
  labs(x = expression(hat(lambda[i])), y = expression(T[i]^{BF})) + theme_minimal()
```


